\documentclass[11pt]{article}
%\usepackage[firstpage]{draftwatermark}
\usepackage{times}
\usepackage{pdfpages}
\usepackage{fullpage}
\usepackage{url}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{indentfirst}
\usepackage{subcaption}
\usepackage{units}

\setcounter{secnumdepth}{4}
\graphicspath{{images/}}
\pagestyle{fancy}

\newcommand{\doctitle}{AUV Control in Waves: Literature Overview}

\addtolength{\headheight}{2em}
\addtolength{\headsep}{1.5em}
\lhead{\doctitle}
\rhead{}

\newcommand{\capt}[1]{\caption{\small \em #1}}

\cfoot{\small Brian Bingham \today \\ \thepage}
\renewcommand{\footrulewidth}{0.4pt}

\newenvironment{xitemize}{\begin{itemize}\addtolength{\itemsep}{-0.75em}}{\end{itemize}}
\newenvironment{tasklist}{\begin{enumerate}[label=\textbf{\thesubsubsection-\arabic*},ref=\thesubsubsection-\arabic*,leftmargin=*]}{\end{enumerate}}
\newcommand\todo[1]{{\bf TODO: #1}}
\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{4}

\makeatletter
\newcommand*{\compress}{\@minipagetrue}
\makeatother

%\renewcommand{\chaptername}{Volume}
%\renewcommand{\thesection}{\Roman{section}}
%\renewcommand{\thesubsection}{\Roman{section}-\Alph{subsection}}

\usepackage{multibib}
\newcites{c,m}%
         {References for AUV Control in Waves,%
           References for AUV models}
         

\begin{document}

\newpage
% Title Page
\setcounter{page}{1}
\begin{center}
{\huge \doctitle}\footnote{Source at \url{https://bitbucket.org/brian_bingham/ocean_notes/src/master/auv_waves_lit.tex}.}
\end{center}


\section{AUV Control in Waves}

\def  \Bibfname {auv_control_waves}

In this section the pertinent literature is listed, roughly in order of relevance.  The quoted text after each citation is the annotation included in \texttt{annote} and/or \texttt{review} fields for each entry in the \texttt{.bib} archive.  The source file is available at \url{https://bitbucket.org/brian_bingham/latexlib/src/master/bib/auv_control_waves.bib}.

The following list of references is in rough order of relevance/recommendation.


\nocitec{dantas13study,datas12auv}
\nocitec{moreira08h2}
\nocitec{willy95attitude}
\nocitec{liu08nonlinear}
\nocitec{riedel98model}
\nocitec{honghan12research}

\bibliographystylec{plain-review}
\bibliographyc{\Bibfname}


\section{AUV Models}

Below are some common models - Prestero's REMUS model seems the most applicable.

\subsection{Prestero}

Popular 6 DOF model of REMUS \citem{prestero01development} \citem{prestero01verification}. Used by \citem{yang16approximate,yang19nonlinear} and other.  Includes tank testing for coefficient identification and V\&V in open water.  Includes linearized control in the depth plane.

\subsection{de Barros}

Diving plane model of AUV Pirajuba with coefficients \citem{dantas12auv} includes references to original de Barros work (2008).  Linearized for LQR/LQG design.

\subsection{Healey}

Linearized diving and steering models for NPS vehicle.
\citem{healey93multi,healey98model}.


\newpage
\setcounter{page}{1}
\bibliographystylem{IEEEtran}
\bibliographym{bbing_master}

\end{document}
